\documentclass[10.5pt]{article}
\usepackage{graphicx}
\setlength{\parindent}{0pt}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=black]{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[left=1.0cm,top=0.75cm,right=1.0cm,bottom=0.6cm]{geometry}
\usepackage{xcolor}
\definecolor{accent}{HTML}{1A5276}
\definecolor{lightaccent}{HTML}{2980B9}

\newcommand{\sectionheader}[1]{
  \vspace{4pt}
  {\color{accent}\textbf{\large #1}}
  \par\vspace{1pt}
  {\color{accent}\hrule}
  \vspace{3pt}
}

\newcommand{\projectlink}[2]{\href{#1}{\color{lightaccent}\underline{\textbf{#2}}}}
\newcommand{\projlink}[2]{\ {\small\projectlink{#1}{#2}}}

\begin{document}

\vspace*{2pt}

\begin{center}
    \textbf{\LARGE\color{accent} Surya Lakavalli}\\ 
    \color{accent}\hrulefill
\end{center}

\begin{center}
    +91 6366582056 \textbullet \ 
    \href{mailto:suryalakavalli@gmail.com}{suryalakavalli@gmail.com} \textbullet \ 
    \href{https://www.linkedin.com/in/surya-lakavalli-4901b4a9/}{linkedin.com/in/surya-lakavalli} \textbullet \ 
    \href{https://github.com/lxkka21}{github.com/lxkka21}
\end{center}

\sectionheader{EDUCATION}

\textbf{Inventure Academy, Bengaluru} \hfill Graduation Date: May 2023 \\
Schooling \hfill 12th Board: 90.12\%

\vspace{4pt}

\textbf{Computer Science Engineering, MIT Manipal} \hfill August 2023 -- Present \\
BTech \hfill CGPA: 7.49

\sectionheader{EXPERIENCE}

\textbf{Research and Development Intern --- GoAI Solutions, Bengaluru} \hfill May -- July 2026
\begin{itemize}[noitemsep, topsep=1pt]
\item Evaluated over 40 AI tools, benchmarking token optimization and agent efficiency within the MCP ecosystem.
\item Analyzed LLM and agent workflow performance, identifying bottlenecks to reduce latency and costs.
\item Refined prompt strategies and model configurations for cost-effective, production-ready agent deployment.
\end{itemize}

\vspace{2pt}

\textbf{Intern --- Schneider Electric, Bengaluru} \hfill May -- July 2025
\begin{itemize}[noitemsep, topsep=1pt]
\item Developed methods to execute natural language queries on Azure Cosmos DB datasets.
\item Worked with Azure services and SQL to improve accessibility and usability of enterprise data.
\end{itemize}

\vspace{2pt}

\textbf{Intern --- Kemp Football Club, Bengaluru} \hfill May -- July 2024
\begin{itemize}[noitemsep, topsep=1pt]
\item Organized and analyzed player performance data across multiple leagues to support scouting decisions.
\item Built datasets from Karnataka and national-level competitions to assist in identifying prospective talent.
\end{itemize}

\sectionheader{PROJECTS}

\textbf{KWL Website}\projlink{https://github.com/lxkka21/KWL-Stats-Website}{GitHub}\projlink{https://kwl-stats.web.app}{Live} \hfill May 2024 -- Present
\begin{itemize}[noitemsep, topsep=1pt]
\item Built a full-stack web application to analyze Karnataka Women's League player statistics across seasons.
\item Implemented advanced filtering, sorting, and search using dynamic Supabase/PostgreSQL queries.
\item Designed a responsive UI for detailed per-player statistical breakdowns and seamless interaction.
\end{itemize}

\vspace{2pt}

\textbf{PosePerfect}\projlink{https://github.com/lxkka21/PosePerfect}{GitHub}\projlink{https://poseperfect-3334c.web.app}{Live} \hfill October -- December 2025
\begin{itemize}[noitemsep, topsep=1pt]
\item Built an AI-powered yoga pose detection app using React.js, Flask, and MediaPipe Pose estimation.
\item Implemented real-time webcam analysis with visual skeleton overlay and per-joint angle feedback across 5 poses.
\item Engineered a pipeline capturing frames every 500ms for live pose correction with 15\textdegree tolerance thresholds.
\end{itemize}

\vspace{2pt}

\textbf{Climate Data System}\projlink{https://github.com/lxkka21/Climate-Data-System}{GitHub} \hfill March -- April 2026
\begin{itemize}[noitemsep, topsep=1pt]
\item Developed a real-time climate data analysis system using external APIs.
\item Implemented visualizations including trend graphs and heatmaps for intuitive insights.
\item Designed the system to support scalable updates and interactive exploration of city-level data.
\end{itemize}

\sectionheader{SKILLS}

\textbf{Languages:} C, Java, SQL \\
\textbf{Tools \& Frameworks:} Azure, Supabase, PostgreSQL, AI Coding Agents, Firebase, Git, Excel

\sectionheader{VOLUNTEER EXPERIENCE}

\textbf{Volunteer}, Asare Centre, Manipal \hfill Jan -- Apr 2026 \\
\hspace*{0.5em} Supported individuals with Down syndrome and intellectual disabilities through structured weekly activities.

\vspace{2pt}

\textbf{Volunteer}, Ramagondanahalli Govt. School \hfill June 2022 -- Mar 2023 \\
\hspace*{0.5em} Taught Math, Science and English to underprivileged children over 9 months.

\vspace{2pt}

\textbf{Volunteer}, Sparsha Trust \hfill June 2019 \\
\hspace*{0.5em} Helped crowdfund ₹18,000 for schooling of an underprivileged youth.

\end{document}
